Synthesis of Linear Functional Programs

### 2021-05-09 article/article.tex
related work graded model types

\mypara{Synthesis from (polymorphic) refinement types}~\cite{DBLP:conf/pldi/PolikarpovaKS16}
This paper also attempts to synthetize recursive functional programs, in a more ``advanced'' setting. The specification
is a combination of two rich types, polymorfic and refinement types (which correspond to a first-order logic through the Curry-Howard isomorphism) -- this is an interesting
combo that offers ``expressive power and decidability, which enables automatic verification--and hence synthesis--of nontrivial programs''.
Their approach to the refinement types is a new algorithm that supports decomposition of the refinement specification,
and they separation between the language of specification and programs.

\mypara{Synthesis for graded types} (no recursion   -- in that work, no
  obvious connection of grading with
  concurrency)~\cite{DBLP:conf/lopstr/HughesO20}

>>>>

\mypara{Program Synthesis from Polymorfic Refinement Types}~\cite{DBLP:conf/pldi/PolikarpovaKS16}
This paper also attempts to synthetize recursive functional programs, in a more ``advanced'' setting. The specification
is a combination of two rich types, polymorfic and refinement types (which correspond to a first-order logic through the Curry-Howard isomorphism) -- this is an interesting
combo that offers ``expressive power and decidability, which enables automatic verification--and hence synthesis--of nontrivial programs''.
Their approach to the refinement types is a new algorithm that supports decomposition of the refinement specification,
and they separation between the language of specification and programs.

\mypara{Resourceful Program Synthesis from Graded Linear Types}~\cite{DBLP:conf/lopstr/HughesO20}
This paper attempts to synthetize programs in a manner very similar to ours.
It uses graded modal types, which is an ``augment'' to linear types -- a more \emph{fine-grained} version, since it allows for
quantitative specification of resource usage, in contrast to ours either \emph{linear} or \emph{unrestricted} (``banged'' values) use of assumptions.
Their resource management is more complex, and so they provide solutions which adapt Hodas and Miller's input-output model~\cite{} -- the model we'll be using.
They also use focusing as a solution to trim down search space, and our solution will use the same literature as a base.
However, since the logic behind the their types is \emph{modal}, instead of \emph{linear}, it doesn't allow to, in the future, explore
the tight relation between linear logic and concurrency based (message passing) programs with session types (e.g. synthetize concurrent programs with message passing), and other fields such as
resource analysis? -- which ours will.

% (no recursion   -- in that work, no
%   obvious connection of grading with
%   concurrency)
